---
title: "Finding a Protein Motif"
author: "G.Robertson"
date: "27/06/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Rosalind problem

Given: At most 15 UniProt Protein Database access IDs.

Return: For each protein possessing the N-glycosylation motif, output its given access ID followed by a list of locations in the protein string where the motif can be found.

Required libraries
```{r}
library(Biostrings)
```

Read in the data
```{r}
ProtMot <- read.table("rosalind_mprt.txt")
```

Loop through the data elements and generate a url for each
```{r}
for(i in ProtMot) {
      fastaURLs = paste0('https://www.uniprot.org/uniprot/',i, '.fasta') # WORKS
      }
```

Loop through list of URLs in fastaURLS and read the AA string from the corresponding webpage
```{r}
x <- list() # initialise a list
for (i in fastaURLs) {
      fastafile <- readAAStringSet(i) 
      seq_name = names(fastafile) 
      seq = paste(fastafile)
      x[i] <- data.frame(seq)
}
```

Extract each sequence element from the list into a dataframe; remove rownames and convert to variable; add protein IDs from which the URLs were generated as a variable and rename columns to produce a table of unique ID's, their fasta webpage and extracted sequences
```{r}
testdf <- data.frame(unlist(x))

testdf1 <- cbind(rownames(testdf), data.frame(testdf, row.names=NULL))

pro_table <- cbind(ProtMot, testdf1)
colnames(pro_table) <- c("ID", "URL", "SEQUENCE")
```

The data is now sourced and in an intuitive format, i.e tabular

Time to find the motif.
The first method of looping through the datatable sequences did not work, and will detail the work done at the end.

```{r}
library(stringi) ## better than stringR as it allows regex indexing
## and therefore can detect overlaps
```

What did work was to find the motif in one sequence at a time using a function:
```{r}
glymot <- function(row){
      cell <- pro_table[row,3]
      strtend <- stri_locate_all_regex(cell, "(?=N[^P][ST][^P])")
      SEdf <- as.data.frame(strtend)
      print(noquote(pro_table[row, 1]))
      print(SEdf$start)
   }
```

To save time, the function calls were written in advance:
```{r}
glymot(1)
glymot(2)
glymot(3)
glymot(4)
glymot(5)
glymot(6)
glymot(7)
glymot(8)
glymot(9)
glymot(10)
glymot(11)
glymot(12)
glymot(13)
glymot(14)
glymot(15)
```

What didn't work....
(It would be great if this loop worked properly)
   
   for (i in testdf1) {
      stend <- str_locate_all(i, pattern = "N[^P][ST][^P]")
   }
