---
title: "Rosalind4"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction to Protein Databases
### From Rosalind Armory

#### Given: The UniProt ID of a protein.
#### Return: A list of biological processes in which the protein is involved (biological processes are found in a subsection of the protein's "Gene Ontology" (GO) section).


Process:
1) Will receive a file with uniProt ID
2) Need to insert protein ID into the uniprot url
3) Summon the uniprot webpage
4) Extract the required information from the specific tag
5) Print this info

```{r}
# read in the file
IDno <- readLines("file.txt")

# insert it into url
protURL = paste0('https://www.uniprot.org/uniprot/',IDno)
protURL
```

The tag was extracted using SelectorGdaget on a representative uniprot page

```{r}
library(rvest)    

protURL %>%
      html_node(".biological_process a") %>%
      html_text()
```

At time of writing, there was an error at Rosalind.com for this problem in that the problem file would not download
